Regional-scale Base-flow Index of Gauged and Ungauged Basins in Drylands

### 2024-12-02 index.qmd
Update index.qmd

Daily observed streamflow data obtained from the United States Geological Survey (USGS) National Water Information System (NWIS) were used in this study. Streamgages were selected depending on criteria to ensure the applicability of each site. @odonnell2016 found that 8-10 years of calibration data were necessary to account for climate variability in paired watershed studies in the region. Following this criteria, a minimum of 10 years of record was chosen. Any years missing more than 30 days of streamflow were removed from the possible record period. This analysis focuses on natural, streamflow-influencing recharge, excluding streamgages affected by regulation or diversions. These gages were identified through annual reports on water data published by the USGS [@usgs2010]. Finally, streamgages on the Colorado River were excluded from the dataset on the basis that they represent managed flows shared by Colorado River Compact states. Following these parameters, 206 USGS streamgages with acceptable periods of record were used in this study (@fig-study-area).

@@

The long-term average BFI for the 244 gauged reaches across Arizona is illustrated in @fig-instrumented-bfi . The highest BFI values (\>0.9) are found along the Grand Canyon in northwestern Arizona. The highly karstic geology of this region facilitates the rapid movement of subsurface flow to surface water and spring outlets [@chambless_deep-karst_2023]. Relatively high BFI values (\>0.8) are found at the spring-fed headwaters of the Verde River (Del Rio Spring) and the spring-fed headwaters of Fossil Creek. These results are consistent with interpolated BFI values reported by @wolock2003.

>>>>

Daily observed streamflow data obtained from the United States Geological Survey (USGS) National Water Information System (NWIS) were used in this study. Streamgages were selected depending on criteria to ensure the applicability of each site. @odonnell2016 found that 8-10 years of calibration data were necessary to account for climate variability in paired watershed studies in the region. Following this criteria, a minimum of 10 years of record was chosen. Any years missing more than 30 days of streamflow were removed from the possible record period. This analysis focuses on natural, streamflow-influencing recharge, excluding streamgages affected by regulation or diversions. These gages were identified through annual reports on water data published by the USGS [@usgs2010]. Finally, streamgages on the Colorado River were excluded from the dataset on the basis that they represent managed flows shared by Colorado River Compact states. Following these parameters, 205 USGS streamgages with acceptable periods of record were used in this study (@fig-study-area).

@@

The long-term average BFI for the 205 gauged reaches across Arizona is illustrated in @fig-instrumented-bfi . The highest BFI values (\>0.9) are found along the Grand Canyon in northwestern Arizona. The highly karstic geology of this region facilitates the rapid movement of subsurface flow to surface water and spring outlets [@chambless_deep-karst_2023]. Relatively high BFI values (\>0.8) are found at the spring-fed headwaters of the Verde River (Del Rio Spring) and the spring-fed headwaters of Fossil Creek. These results are consistent with interpolated BFI values reported by @wolock2003.
